Enzo+Moray: Radiation Hydrodynamics Adaptive Mesh Refinement Simulations with Adaptive Ray Tracing

### 2010-08-20 ms.tex
Wrote the summary.

>>>>

In this paper, we have presented our implementation of adaptive ray
tracing \citep{Abel02_RT} and its coupling to the hydrodynamics in the
cosmology AMR code \enzo, making it a fully functional radiation
hydrodynamics code.  As this method is photon conserving, accurate
solutions are possible with coarse spatial resolution.  A new
geometric correction factor to ray tracing on a Cartesian grid was
described, and it is general to any implementation.  We have
exhaustively tested the code to problems with known analytical
solutions and the problems presented in the RT06 and RT09 radiative
transfer comparison papers.  Additionally we have tested our code with
more dynamical problems---champange flows, Rayleigh-Taylor
instabilities, photo-evaporation of a blastwave, beamed radiation, a
time-varying source, and an \ion{H}{2} region with MHD---to
demonstrate the flexibility and fidelity of Enzo+Moray.  Because
production simulations may not have the resolution afforded in these
test problems, we have tested the dependence on spatial, angular,
frequency, and temporal resolution.  It provides accurate solutions
even at low resolution, except for the large constant timesteps.
However, we have described two methods to determine the radiative
transfer timestep that are based on the variations in specific
intensity or changes in neutral fraction inside the ionization front.
Both methods give very accurate results and provide the largest
timestep to obtain an accurate solution, ultimately leading to higher
computational efficiency.  On the same topic, we have described a
method to calculate the radiation field in the optically-thin limit
with ray tracing.

Being a ray tracing code, it scales with the number of radiation
sources, albeit lessened with ray merging; nevertheless, it scales
well to O($10^3$) processors for problems with $\sim10^9$
computational cells and $\sim10^4$ sources, such as reionization
calculations.  We have also shown that the code shows good strong
scaling in AMR calculations, given a large enough problem.  The
combination of the AMR and adaptive ray tracing allows for
high-resolution and high-dynamical range problems, e.g. molecular
cloud resolving galaxy formation simulations and \ion{H}{2} regions of
Population III stars.  Furthermore, we have included Lyman-Werner
absorption, secondary ionizations from X-ray radiation, Compton
heating from photon scattering, and radiation pressure, into the code,
which extends the reach of Enzo+Moray to study AGN feedback, stellar
winds, and local star formation.  Coupling the radiative transfer with
MHD further broadens the applicability of our code.  The full
implementation is included in the latest public version of
\enzo\footnote{http://lca.ucsd.edu/enzo}, providing the community with
a full-featured radiation hydrodynamics AMR code.
